---
title: "30535 Skills Problem Set 3"
author: "Sabarish Shankar"
date: "25/04/2020"
output:
  html_document:
    #number_sections: yes
  pdf_document: default
---
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(dplyr)
```

# Front matter
This submission is my work alone and complies with the 30535 integrity policy.

Add your initials to indicate your agreement: **Sabarish Shankar**

Add your collaborators: **__**

Late coins used this pset: 0. Late coins left: 4. 

FEEDBACK from PS 2: Thank you for explaining your reasoning. I don't think net delay is as practical as arrival delay is alone - if a plane leaves 30 minutes late and arrives 30 minutes late, the effect of the delay is 30 minutes and not an hour.
FEEDBACK: See solutions.

# 2. R for Data Science Exercises
## 2.1 Transformations: Grouped operations with mutate() (and filter()) (20
points)


1. 

```{r}
flights <- nycflights13::flights
summary(flights)
View(flights)
flights%>% arrange(origin, dest, day, sched_dep_time)%>%
  select(tailnum, origin, dest, day, sched_dep_time, dep_delay)%>%
  group_by(origin)%>%
  mutate(lag_delay = lag((sched_dep_time)))

```

2. 

```{r}

```

3. 

```{r}

```

## 2.2 Exploratory Data Analysis (25 points)

### 2.2.1 EDA: Exploring variation


```{r}

```

### 2.2.2 EDA: Navigating NAs

```{r}

```

# 3 Exploratory Data Analysis: Covariation (35 points)

1.

```{r}

```

2. 

```{r}

```

```{r}

```

```{r}

```

```{r}

```